\documentclass[a4paper,10pt]{article}

\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

%-------------------- HEADER --------------------
\begin{center}
    {\LARGE \textbf{Rupjyoti Barman}} \\
    Guwahati \\
    \href{mailto:rupjyoti921@gmail.com}{rupjyoti921@gmail.com} \quad | \quad +91-9101171366 \\
    LinkedIn \quad | \quad GitHub
\end{center}

%-------------------- SKILLS --------------------
\section*{Technical Skills}

\begin{itemize}[leftmargin=*]
    \item \textbf{Languages:} C\#, C++, C, Python, JavaScript, PHP, SQL
    
    \item \textbf{Technologies \& Tools:} .NET, ASP.NET Core Web API, ASP.NET MVC, Entity Framework Core, PostgreSQL, MySQL, MongoDB, Bootstrap, NumPy, Pandas, Matplotlib, Scikit-learn, Git, SVN, Jira, Miro, Confluence, TestRail
\end{itemize}

%-------------------- EXPERIENCE --------------------
\section*{Experience}

\textbf{Software Developer, BoldTek India Pvt. Ltd. – Guwahati} \hfill June 2023 -- Present

\begin{itemize}[leftmargin=*]

\item Designed and developed hardware diagnostic APIs using C\# in a layered architecture, where business logic interacts with native C++ DLLs to execute low-level hardware tests. Enabled seamless communication between managed and unmanaged components for real-time diagnostics.

\item Implemented diagnostic modules including SMART health checks, disk read/verify operations, sleep/wake validation, IRQ validation, and ROM-based MAC address verification, ensuring system reliability and hardware stability.

\item Integrated Windows Update Agent (WUA) API to programmatically scan, retrieve, and install driver updates from Microsoft servers, improving system maintenance and reducing manual intervention.

\item Automated BIOS updates using HP Client Management Script Library (HPCMSL) via PowerShell, streamlining firmware upgrades across enterprise devices.

\item Built real-time device monitoring using WMI by querying Plug-and-Play devices and subscribing to hardware events, enabling dynamic detection of device insertion and removal.

\item Contributed to migration of multiple components from .NET 6 to .NET 9, resolving compatibility issues and leveraging modern framework enhancements.

\item Led architectural improvement by decoupling dependency on an external diagnostic service. Packaged business logic, API layer, and native C++ DLLs into a unified NuGet package enabling local execution.

\item Eliminated dependency on external service release cycles, significantly improving development velocity and reducing delays in feature delivery.

\item Applied design patterns such as Facade and implemented Dependency Injection extensively to improve modularity, maintainability, and scalability.

\item Worked on an ASP.NET Core MVC application managing INI configuration files, improving UI/UX and implementing regex-based validation for structured data.

\item Developed full-stack features including CRUD operations and role-based access control (User, Developer, Admin) for managing version-based configuration data.

\item Contributed across controller, service, and repository layers, ensuring clean architecture and efficient data flow.

\item Worked with RPC-based service architecture for executing diagnostics remotely and later optimized it by transitioning to local execution.

\item Collaborated with cross-functional global teams (India, Taiwan, US) to deliver features, debug issues, and ensure smooth integration.

\end{itemize}

%-------------------- PROJECTS --------------------
\section*{Projects}

\textbf{Ticket Management System (ASP.NET Core Web API)}

\begin{itemize}[leftmargin=*]
\item Developed a production-ready backend using ASP.NET Core Web API following SOLID principles and clean layered architecture (Controller–Service–Repository).

\item Integrated PostgreSQL using Entity Framework Core and designed relational database models with proper entity relationships.

\item Implemented JWT-based authentication and role-based authorization (User, Agent, Admin) to secure APIs.

\item Built scalable REST APIs supporting complete ticket lifecycle (create, assign, update, delete) using DTO-based architecture, validation, global exception handling, and dependency injection.

\item Implemented structured logging using Serilog for better debugging and monitoring of application behavior.
\end{itemize}

\textbf{Grade Prediction using Machine Learning}

\begin{itemize}[leftmargin=*]
    \item Developed a machine learning model using linear and logistic regression to predict student performance based on internal assessment data.
    
    \item Used NumPy, Pandas, Matplotlib, and Scikit-learn for data preprocessing, visualization, and model training.
    
    \item Analyzed student data patterns to generate predictive insights and improve accuracy of grade estimation.
\end{itemize}

%-------------------- EDUCATION --------------------
\section*{Education}

\textbf{B.Tech in Computer Science \& Engineering} \hfill Aug 2020 -- May 2023 \\
North Eastern Regional Institute of Science and Technology (NERIST), Arunachal Pradesh

\end{document}